\chapter{Almost purity}    
    \section{Almost ring theory}
        \subsection{Almost modules}
            \begin{convention}[\say{Basic setups}] \label{conv: basic_setups}
                A \textbf{basic setup} for us shall always be a pair $(\scrV, \m)$ consisting of a commutative ring $\scrV$ along with an idempotent ideal $\m$ (i.e. one such that $\m^2 = \m$; note that this ideal need not be maximal, despite what our notation might suggest). One often speaks also of \textbf{flat basic setups}, which are basic setups $(\scrV, \m)$ such that $\m$ is flat over $\scrV$; such a specification can be made to ensure that the functor $- \tensor_{\scrV} \m$ is exact.
            \end{convention}
            
            \begin{definition}[Almost zero modules] \label{def: almost_zero_modules}
                Let $(\scrV, \m)$ be a basic setup (cf. convention \ref{conv: basic_setups}) and fix a $\scrV$-algebra. Then, a $\scrV$-module $M$ (or should the situation calls for speification, a $(\scrV, \m)$-module $M$) is said to be \textbf{almost zero} if and only if it is annihilated by $\m$, i.e.:
                    $$\m M = 0$$
            \end{definition}
            \begin{lemma} \label{lemma: tensor_powers_of_flat_modules}
                Let $R$ be a commutative ring and let $N$ be a flat $R$-module. Then, $N \tensor_R N$ is also flat. Also, for all $R$-ideals $\m$, one has:
                    $$\m \tensor_R M \cong \m M$$
            \end{lemma}
                \begin{proof}
                    If $N$ is flat over $R$ then the functor $- \tensor_R N$ will be left-exact. The composition of two left-exact is again left-exact for trivial reasons. Thus $N \tensor_R N$ is flat over $R$.
                    
                    As for the assertion that $\m \tensor_R M \cong \m M$ whenever $\m$ is flat, we can rely on homological algebra. Specifically, because $\m$ is flat, we have:
                        $$\m M \cong \Tor_R^1(\m, M) \cong 0$$
                \end{proof}
            \begin{proposition}[Another definition of almost zero modules] \label{prop: almost_zero_module_alt_def}
                Let $(\scrV, \m)$ be a \textit{flat} basic setup (cf. convention \ref{conv: basic_setups}) and fix a $\scrV$-algebra. Then, a $\scrV$-module $M$ is said to be \textbf{almost zero} if and only if:
                    $$\m \tensor_{\scrV} M  \cong0$$
            \end{proposition}
                \begin{proof}
                    \noindent
                    \begin{enumerate}
                        \item Suppose first of all that $M$ is \textit{non zero} and almost zero, i.e. that $\m M \cong 0$. Then, a direct application of lemma \ref{lemma: tensor_powers_of_flat_modules} (which is appropriate because $\m$ is flat over $\scrV$) tells us that:
                            $$0 \cong \m M \cong \m \tensor_{\scrV} M$$
                        \item Conversely, suppose that $\m \tensor_{\scrV} M \cong 0$. Because $\m$ is flat over $\scrV$, this tells us that there exists the following short exact sequence:
                            $$0 \to \m \tensor_{\scrV} \m M \to 0 \to M/\m M \tensor_{\scrV} \m \to 0$$
                        Using some abstract nonsense, we can then see that:
                            $$\m \tensor_{\scrV} \m M \cong 0$$
                        We can apply the flatness assumption on $\m$ again, which gives:
                            $$0 \cong \m \tensor_{\scrV} \m M \cong (\m \tensor_{\scrV} \m) M \cong \m^2 M$$
                        Lastly, because $\m$ is idempotent, the above implies that:
                            $$0 \cong \m^2 M = \m M$$
                        i.e. $M$ is almost zero as a $\scrV$-module.
                    \end{enumerate}
                \end{proof}
                
            \begin{proposition}[Thick subcategories of almost zero modules] \label{prop: thick_subcategories_of_almost_zero_modules}
                Let $(\scrV, \m)$ be a flat basic setup. Then, almost zero $\scrV$-modules form a thick subcategory of $\scrV\mod$, which we shall denote by $(\scrV, \m)\mod^0$.
            \end{proposition}
                \begin{proof}
                    \noindent
                    \begin{enumerate}
                        \item \textbf{(Full subcategories of almost zero modules):} Let $M, N$ be two almost zero $(\scrV, \m)$-modules. Then, because:
                            $$\m M \cong \m N \cong 0$$
                        we have:
                            $$M \cong M/\m M, N \cong N/\m N$$
                        and so any diagram of the following form, wherein the rows are short exact sequences, would commute:
                            $$
                                \begin{tikzcd}
                                	0 & {\m M} & M & {M/\m M} & 0 \\
                                	0 & {\m N} & N & {N/ \m N} & 0
                                	\arrow[from=1-1, to=1-2]
                                	\arrow[from=1-2, to=1-3]
                                	\arrow[from=1-3, to=1-4]
                                	\arrow[from=1-4, to=1-5]
                                	\arrow[from=2-1, to=2-2]
                                	\arrow[from=2-2, to=2-3]
                                	\arrow[from=2-3, to=2-4]
                                	\arrow[from=2-4, to=2-5]
                                	\arrow[from=1-2, to=2-2]
                                	\arrow[from=1-3, to=2-3]
                                	\arrow[from=1-4, to=2-4]
                                \end{tikzcd}
                            $$
                        From this, we can infer that morphisms of almost zero module are just module homomorphisms, which means that there exists a full subcategory $(\scrV, \m)\mod^0$ of $\scrV\mod$ spanned by almost zero $(\scrV, \m)$-modules.
                        \item \textbf{(Thickness):} A \textit{full} subcategory $\S$ of a triangulated category $\T$; our triangulated category is $\scrV\mod$) is said to be \textbf{thick} whenever it is closed under extensions, which is to say, for all short exact sequences:
                            $$0 \to M' \to M \to M'' \to 0$$
                        should $M$ be an object of $\S$, then so must $M'$ and $M''$ too, and vice versa (one might also think of a thick subcategory as the homotopy category of a stable full $\infty$-subcategory of a triangulated $\infty$-category). We already have fullness, so it remains to show that $(\scrV, \m)\mod^0$ is closed under extensions. To this end, consider a short exact sequence of $\scrV$-modules, such as the following:
                            $$0 \to M' \to M \to M'' \to 0$$
                        wherein $M$ is almost zero. Then, because binary direct sums of modules are biproducts and because $\m$ is flat over $\scrV$, one can construct the following diagram with short exact rows out of the short exact sequence above:
                            $$
                                \begin{tikzcd}
                                	0 & {\m \tensor_{\scrV} M'} & {\m \tensor_{\scrV} (M' \oplus M'')} & {\m \tensor_{\scrV} M''} & 0 \\
                                	0 & {\m \tensor_{\scrV} M'} & {\m \tensor_{\scrV} M} & {\m \tensor_{\scrV} M''} & 0 \\
                                	0 & {\m \tensor_{\scrV} M'} & {\m \tensor_{\scrV} (M' \oplus M'')} & {\m \tensor_{\scrV} M''} & 0
                                	\arrow[from=1-1, to=1-2]
                                	\arrow[from=1-2, to=1-3]
                                	\arrow[from=1-3, to=1-4]
                                	\arrow[from=1-4, to=1-5]
                                	\arrow[from=2-1, to=2-2]
                                	\arrow[from=2-2, to=2-3]
                                	\arrow[from=2-3, to=2-4]
                                	\arrow[from=2-4, to=2-5]
                                	\arrow[from=3-1, to=3-2]
                                	\arrow[from=3-2, to=3-3]
                                	\arrow[from=3-3, to=3-4]
                                	\arrow[from=3-4, to=3-5]
                                	\arrow["{=}"{description}, from=2-2, to=3-2]
                                	\arrow[dashed, tail, from=1-3, to=2-3]
                                	\arrow[dashed, two heads, from=2-3, to=3-3]
                                	\arrow["{=}"{description}, from=1-4, to=2-4]
                                	\arrow["{=}"{description}, from=2-4, to=3-4]
                                	\arrow["{=}"{description}, from=1-2, to=2-2]
                                \end{tikzcd}
                            $$
                        We can reuse the flatness assumption on $\m$ again (specifically, lemma \ref{lemma: tensor_powers_of_flat_modules}, which implies that $\m \tensor_{\scrV} M' \cong \m M'$ and $\m \tensor_{\scrV} M'' \cong \m M''$) as well as the assumption that $M'$ and $M''$ are almost zero, and the fact that tensor products commute with finite direct sums, to condense the above diagram into:
                            $$
                                \begin{tikzcd}
                                	0 & 0 & 0 & 0 & 0 \\
                                	0 & 0 & {\m M} & 0 & 0 \\
                                	0 & 0 & 0 & 0 & 0
                                	\arrow[from=1-1, to=1-2]
                                	\arrow[from=1-2, to=1-3]
                                	\arrow[from=2-1, to=2-2]
                                	\arrow[from=2-2, to=2-3]
                                	\arrow[dashed, tail, from=1-3, to=2-3]
                                	\arrow[dashed, two heads, from=2-3, to=3-3]
                                	\arrow[from=1-2, to=2-2]
                                	\arrow[from=2-2, to=3-2]
                                	\arrow[from=3-1, to=3-2]
                                	\arrow[from=3-2, to=3-3]
                                	\arrow[from=1-3, to=1-4]
                                	\arrow[from=1-4, to=1-5]
                                	\arrow[from=2-3, to=2-4]
                                	\arrow[from=2-4, to=2-5]
                                	\arrow[from=1-4, to=2-4]
                                	\arrow[from=2-4, to=3-4]
                                	\arrow[from=3-3, to=3-4]
                                	\arrow[from=3-4, to=3-5]
                                \end{tikzcd}
                            $$
                        We can now easily deduce that $\m M \cong 0$, i.e. that $M$ is almost zero. This tells us that the full subcategory $(\scrV, \m)\mod^0$ is closed under extensions, and thus thick by definition.
                    \end{enumerate}
                \end{proof}
            \begin{remark}[Almost zero modules over non-flat basic setups] \label{remark: almost_zero_modules_over_non_flat_basic_setups}
                \noindent
                \begin{itemize}
                    \item \textbf{(Removing the flatness assumption):} Proposition \ref{prop: thick_subcategories_of_almost_zero_modules} allows us to pull off quite a stunt, and for that matter, not even with much difficulty: the flatness assumption on $\m$ can be completely removed! Of course, the trade-off is that now, only the $\infty$-categorical version of proposition \ref{prop: thick_subcategories_of_almost_zero_modules} would hold: via the Dold-Kan Correspondence, one has that for $(\scrV, \m)$ a basic setup, $\scrV$-modules annihilated by $\m$ span a stable full $\infty$-subcategory $(\scrV, \m)\mod^0$ (or perhaps ${}^{\leq 0}_{(\scrV, \m)}\mod^0$) of the triangulated $\infty$-category ${}^{\leq 0}_{\scrV}\mod$ of projective resolutions of $\scrV$-modules. This descends naturally down to the level of derived categories. One can thus generalise proposition \ref{prop: almost_zero_module_alt_def} too: a $\scrV$-module is almost zero if and only if:
                        $$\m \tensor_{\scrV}^{\L} M \cong_{\qis} 0$$
                    (i.e. the chain complex $\Tor_{\scrV}^*(\m, M)$ is homotopic to $0$).
                    \item \textbf{(Abelian categories of almost zero modules):} If we extract the hearts of the t-structures out of ${}^{\leq 0}_{(\scrV, \m)}\mod^0$ and ${}^{\leq 0}_{\scrV}\mod$, we will be able to establish ${}^{\leq 0}_{(\scrV, \m)}\mod^{\almost, \heart}$ as a Serre subcategory of ${}^{\leq 0}_{\scrV}\mod^{\heart}$, and since hearts of t-structure are spanned by objects concentrated in degree $0$, one can furthurmore recognise ${}^{\leq 0}_{(\scrV, \m)}\mod^0$ as a Serre subcategory of $\scrV\mod$ whenever the basic setup $(\scrV, \m)$ is \textit{flat}. In particular, we have that the thick subcategories of almost zero modules are \textit{abelian}.
                \end{itemize}
            \end{remark}
            
            \begin{definition}[Almost modules] \label{def: almost_modules}
                Let $(\scrV, \m)$ be a basic setup. Then, the essential image of the functor:
                    $$\m \tensor_{\scrV}^{\L} -: {\scrV}^{\leq 0}\mod \to {\scrV}^{\leq 0}\mod$$
                (i.e. the category spanned by objects of the form $\m \tensor_{\scrV}^{\L} M$, where $M$ is a $\scrV$-module) shall be called the category of \textbf{almost modules}. We shall denote this category by ${(\scrV, \m)}^{\leq 0}\mod^{\almost}$.
            \end{definition}
            \begin{remark}[Categories of almost zero modules are kernels] \label{remark: categories_of_almost_zero_modules_are_kernels}
                It is not hard to see that for $(\scrV, \m)$ a basic setup, the category ${(\scrV, \m)}^{\leq 0}\mod^0$ of almost zero $(\scrV, \m)$-modules is the kernel or the essentially surjective functor:
                    $$\m \tensor_{\scrV}^{\L} -: {\scrV}^{\leq 0}\mod \to {(\scrV, \m)}^{\leq 0}\mod^{\almost}$$
                Note that this kernel is well-defined because $\m \tensor_{\scrV}^{\L} -$ is an idempotent functor (cf. remark \ref{remark: almost_zero_modules_over_non_flat_basic_setups}).
            \end{remark}
            
            \begin{proposition}[Localising at almost modules] \label{prop: localising_at_almost_modules}
                Let $(\scrV, \m)$ be a basic setup (which need not be flat). Then, the tensor-hom adjunction establishes ${(\scrV, \m)}^{\leq 0}\mod^{\almost}$ as a localisation. This is to say, there exists the following $\infty$-adjunction:
                    $$
                        \begin{tikzcd}
                        	{{(\scrV, \m)}^{\leq 0}\mod^{\almost}} & {{\scrV}^{\leq 0}\mod}
                        	\arrow[""{name=0, anchor=center, inner sep=0}, "{j_*}"', shift right=2, hook, from=1-1, to=1-2]
                        	\arrow[""{name=1, anchor=center, inner sep=0}, "{j^*}"', shift right=2, from=1-2, to=1-1]
                        	\arrow["\dashv"{anchor=center, rotate=-90}, draw=none, from=1, to=0]
                        \end{tikzcd}
                    $$
                wherein $j^* \cong \m \tensor_{\scrV}^{\L} -$ and $j_*(-) \cong \R\Hom_{\scrV}(\m, -)$.
            \end{proposition}
                \begin{proof}
                    The only thing to prove here is that $j_*$ ought to be fully faithful, which we can do via showing that the counit of the adjunction is naturally isomorphic to the identity; explicitly, this means showing that for all almost zero $(\scrV, \m)$-modules $M$, one has the following isomorphism:
                        $$j^* j_* M \cong M$$
                    However, this is an automatic consequence of the fact that ${(\scrV, \m)}^{\leq 0}\mod^{\almost}$ is the essential image of $j^*: {\scrV}^{\leq}\mod \to {\scrV}^{\leq}\mod$.
                \end{proof}
            
            \begin{theorem}[Four functors for almost modules] \label{theorem: four_functors_for_almost_modules}
                Let $(\scrV, \m)$ be a \textit{flat} basic setup. Then, the usual four-functor pull-push yoga is applicable to almost modules over \textit{flat} basic setups, in the sense that one has the following adjunction quadruple:
                    $$
                        \begin{tikzcd}
                        	{{\scrV}^{\leq 0}\mod} & {{(\scrV, \m)}^{\leq 0}\mod^{\almost}}
                        	\arrow[""{name=0, anchor=center, inner sep=0}, "{j_! \ladjoint j^* \ladjoint j_* \ladjoint j^!}"', shift right=5, from=1-2, to=1-1]
                        	\arrow[""{name=1, anchor=center, inner sep=0}, shift right=5, from=1-1, to=1-2]
                        	\arrow[""{name=2, anchor=center, inner sep=0}, shift left=2, from=1-2, to=1-1]
                        	\arrow[""{name=3, anchor=center, inner sep=0}, shift left=2, from=1-1, to=1-2]
                        	\arrow["\dashv"{anchor=center, rotate=-90}, draw=none, from=0, to=3]
                        	\arrow["\dashv"{anchor=center, rotate=-90}, draw=none, from=3, to=2]
                        	\arrow["\dashv"{anchor=center, rotate=-90}, draw=none, from=2, to=1]
                        \end{tikzcd}
                    $$
                wherein $j^* \cong \m \tensor_{\scrV}^{\L} -$ and $j_*(-) \cong \R\Hom_{\scrV}(\m, -)$.
            \end{theorem}
                \begin{proof}
                    We have already been provided with the middle adjunction $j^* \ladjoint j_*$, so let us just prove that the $!$-pushforwards and $!$-pullbacks exist and fit into the following adjunctions:
                        $$j_! \ladjoint j^*$$
                        $$j_* \ladjoint j^!$$
                    Although, we should note that we can have $j^* \cong \m \tensor_{\scrV}^{\L} -$ and $j_*(-) \cong \R\Hom_{\scrV}(\m, -)$ as two of the basic \href{https://ncatlab.org/nlab/show/six+operations}{\underline{four operations}} because ${(\scrV, \m)}^{\leq 0}\mod^{\almost}$ is the essential image of a functor out of ${\scrV}^{\leq 0}\mod$ (cf. proposition \ref{prop: localising_at_almost_modules}). 
                        \begin{enumerate}
                            \item \textbf{($!$-pushforward):} To show that the further left-adjoint $j^!$ exists, we will be using Lurie's Adjoint Functor Theorem \cite[Corollary 5.5.2.9]{HTT}, which states that should $\C$ and $\D$ be presentable $\infty$-categories and $R: \C \to \D$ be a functor between them, then there exists an adjunction $L \ladjoint R$ if and only if $R$ is accessible (i.e. $R$ preserves all filtered colimits) and left-exact. For this, we will first need to show that ${(\scrV, \m)}^{\leq 0}\mod^{\almost}$ is a presentable $\infty$-category (it is well-known that module categories like ${\scrV}^{\leq 0}\mod$ are presentable, so we will not be providing a proof).
                                \begin{enumerate}
                                    \item \textbf{(${(\scrV, \m)}^{\leq 0}\mod^{\almost}$ is presentable):} Recall that a presentable stable $\infty$-category is the same as an $\infty$-category that is:
                                        \begin{itemize}
                                            \item accessible and
                                            \item equivalent to a left-exact localisation (i.e a left-exact functor with a full faithful right-adjoint) of a stable $\infty$-category.
                                        \end{itemize}  
                                        
                                    The second condition is an automatic consequence of proposition \ref{prop: localising_at_almost_modules} and the assumption that $\m$ is flat (which means, by definition, that $j^*(-) \cong \m \tensor_{\scrV} -$ is a left-exact functor), and so it remains to prove the first      condition. 
                                    
                                    For this, consider a filtered colimit:
                                        $$\underset{i \in I}{\colim} (\m \tensor_{\scrV}^{\L} M_i)$$
                                    of almost $(\scrV, \m)$-modules $\m \tensor_{\scrV}^{\L} M_i$ (see proposition \ref{prop: localising_at_almost_modules} for why almost modules are of this form). We can then apply the fact that $\m \tensor_{\scrV}^{\L} -$ commutes with all colimits to get:
                                        $$\m \tensor_{\scrV}^{\L} \underset{i \in I}{\colim} (\m \tensor_{\scrV}^{\L} M_i) \cong \m \tensor_{\scrV}^{\L} \underset{i \in I}{\colim} M_i$$
                                    Because ${\scrV}^{\leq 0}\mod$ is a cocomplete category (which implies, in particular, that $\underset{i \in I}{\colim} M_i$ is a $\scrV$-module), this tells us that ${(\scrV, \m)}^{\leq 0}\mod^{\almost}$ is closed under filtered colimits. 
                                    
                                    The category ${(\scrV, \m)}^{\leq 0}\mod^{\almost}$ is thus accessible by definition, and we have therefore shown that ${(\scrV, \m)}^{\leq 0}\mod^{\almost}$ is presentable as an $\infty$-category.
                                    \item \textbf{($j^*$ is accessible):} Because tensor products commute with all colimits, $j^*$ is trivially accessible by virtue of being naturally isomorphic to $\m \tensor_{\scrV}^{\L} -$. 
                                    \item \textbf{($j^*$ is left-exact):} This is an automatic consequence of the flatness assumption on $\m$.
                                \end{enumerate}
                            \item \textbf{($!$-pullback):} We have already shown that ${(\scrV, \m)}^{\leq 0}\mod^{\almost}$ is a presentable $\infty$-category, so we can apply Lurie's Adjoint Functor Theorem again, which tells us that we will only need to show that $j_*$ is right-exact. However, because corepresentable functors preserve colimits \textit{a priori} (cf. \cite{nlab:hom-functor_preserves_limits}), the functor:
                                $$j_* \cong \R\Hom_{\scrV}(\m, -)$$
                            is trivially right-exact.
                        \end{enumerate}
                \end{proof}
                
            \begin{proposition}[Tensor products of almost modules] \label{prop: tensor_products_of_almost_modules}
                Let $(\scrV, \m)$ be a basic setup. Then, ${(\scrV, \m)}^{\leq 0}\mod^{\almost}$ is a rigid monoidal category; in particular, there is a compatibility of tensor products in the following manner for all $\scrV$-modules $M$ and $N$:
                    $$j^*M \tensor^{\L}_{\scrV} j^*N \cong j^*(M \tensor^{\L}_{\scrV} N)$$
                where $j^*$ is as in proposition \ref{prop: localising_at_almost_modules} and theorem \ref{theorem: four_functors_for_almost_modules}; the monoidal unit is $\m$.
            \end{proposition}
                \begin{proof}
                    
                \end{proof}
            \begin{convention}[Almost tensor products] \label{conv: almost_tensor_products}
                Let $(\scrV, \m)$ be a basic setup. Then for all $M, N \in {\scrV}^{\leq 0}\mod$, let us abbreviate the quasi-isomorphism:
                    $$j^*M \tensor^{\L}_{\scrV} j^*N \cong j^*(M \tensor^{\L}_{\scrV} N)$$
                by:
                    $$M^{\almost} \tensor^{\L}_{\scrV} N^{\almost} \cong (M \tensor^{\L}_{\scrV} N)^{\almost}$$
                whenever the underlying basic setup $(\scrV, \m)$ is understood.
            \end{convention}
            \begin{remark}[(In)compatibility of monoidal structures] \label{remark: incompatible_monoidal_structures_almost_modules}
                Let $(\scrV, \m)$ be a basic setup, which is possible non-flat.
                \begin{itemize}
                    \item \textbf{(Tensor products of almost modules):} ${\scrV}^{\leq 0}\mod$ does \textit{not} admit ${(\scrV, \m)}^{\leq 0}\mod^{\almost}$ as a \textit{monoidal} subcategory, as the monoidal structures thereon are formed differently; in particular, their monoidal units ($\scrV$ and $\m$ respectively) do not coincide.
                    \item \textbf{(Tensor products of almost zero modules):} The story is not quite the same for almost zero modules, which form a subcategory of ${\scrV}^{\leq 0}\mod$. Thanks to the assumption that $\m$ is idempotent (in the sense that $\m \tensor_{\scrV}^{\L} \m \cong \m$; cf. convention \ref{conv: basic_setups} and remark \ref{remark: almost_zero_modules_over_non_flat_basic_setups}), one has the following for all almost zero modules $M, N$:
                        $$\m \tensor_{\scrV}^{\L} (M \tensor_{\scrV}^{\L} N) \cong (\m \tensor_{\scrV}^{\L} \m) \tensor_{\scrV}^{\L} (M \tensor_{\scrV}^{\L} N) \cong (\m \tensor_{\scrV}^{\L} M) \tensor_{\scrV}^{\L} (\m \tensor_{\scrV}^{\L} N) = 0 \tensor_{\scrV}^{\L} 0 \cong 0$$
                    which proves that ${(\scrV, \m)}^{\leq 0}\mod^0$ is a monoidal subcategory of ${\scrV}^{\leq 0}\mod$. 
                \end{itemize}
            \end{remark}
            
            \begin{definition}[Almost flatness] \label{def: almost_flatness}
            
            \end{definition}
            
        \subsection{Almost \'etale extensions}
    
    \section{Perfectoid spaces}
        \subsection{Introduction}
            Originally, perfectoid spaces were introduced by Peter Scholze in 2011 with the purpose of proving the Weight-Monodromy Conjecture of Pierre Deligne in mind (cf. \cite{scholze2011perfectoid}). As it turns out, however, perfectoid spaces have much further-reaching applications, particularly in the context of the Langlands Programme, wherein certain perfectoid spaces (namely the Fargues-Fontaine Curve) play crucial roles and serve as analogues of curves over function fields or over the complex numbers, over which many important (geometric) results have been established. 
    	    
    	    To begin to make sense of this statement, however, let us first remark that perfectoid spaces form a particular class of so-called adic spaces, which are non-archimedean mirror images of complex manifolds. The study of adic spaces (and special types thereof, such as rigid analytic varieties, which are to adic spaces what varieties are to schemes) is known as \textbf{rigid-analytic geometry}, and the reason that adic spaces are similar to complex manifolds is that in rigid-analytic geometry, there are many theorems that bare remarkable resemblances to those that relate scheme-theoretic algebraic geometry and complex-analytic geometry. Notably, one has a non-archimedean version of Serre's GAGA Theorem, and one has many comparison theorems which form the backbone of the field known as \textbf{$p$-adic Hodge theory} (and as the name suggests, mimics classical complex Hodge theory).
    	    
    	    Now, one of the issues with the category of adic spaces (and to a similar extent, with the subcategory of rigid-analytic varieties) is that it is not particularly well-behaved, at least from a structuralist's point of view. For instance, not even pullbacks exist all the time; one usually would need to impose certain finiteness conditions to guarantee that these limits would exist, but these impositions can make the theory rather rigid\footnote{No pun intended} and hard to work with\footnote{This is not even to mention that many important classes of adic spaces are infinite-dimensional: perfectoid spaces, for instance, are usually not even Noetherian!}. This is a rather serious issue, because without pullbacks, one therefore finds oneself at a lost when it comes to establishing good notions of base-change and moduli spaces, which time and time again have proven themselves to be very powerful tools. Grothendieck himself, in fact, taught us that schemes should never be thought of as static absolute objects, but rather, relative objects whose fibres over appropriate algebraically closed fields are algebraic varieties in the classical sense. And the story is not too much different in the world of rigid-analytic geometry: now, adic spaces play the role of schemes, and rigid-analytic varieties play the role of algebraic varieties. Another issue with the category of adic spaces is that it can be rather hard to know if the structure sheaf $\calO_X$ of a given topologically ringed space $(X, \calO_X)$ admits a subpresheaf $\calO_X^+$ which is simultaneously a sheaf and satisfy certain number-theoretically motivated topololgical conditions (in such a case, one says that the pair $(\calO_X, \calO_X^+)$ is \textbf{sheafy}).   
    	    
    	    This is the point at which perfectoid spaces come to the rescue. For somewhat non-trivial reasons, the subcategory spanned by perfectoid spaces of the category of adic spaces is much more nicer. In particular, it admits all finite pullbacks\footnote{In fact, the category of perfectoid spaces admit affinoid filtered limits along with other universal constructions that one has for schemes, too. For instance, the notion of open and closed immersion are both well-defined for perfectoid spaces (the latter is not so for adic spaces).} (cf. \cite[Proposition 6.18]{scholze2011perfectoid}) and as one can guess (seeing how the category of perfectoid spaces is a subcategory of the category of adic spaces), all perfectoid spaces are sheafy. As such, perfectoid spaces can be thought of as adic spaces which behave - at least categorically speaking - very similarly to schemes. 
    	    
        \subsection{Perfectoid geometry}
            \subsubsection{Perfectoid fields}
    	        Let us first establish the Tilting Equivalence at the level of \'etale sites of perfectoid fields. One should think of this equivalence as  
    	    
        	    \begin{definition}[Perfectoid rings] \label{def: perfectoid_rings}
                    A \textit{complete} Tate ring $R$ is \textbf{perfectoid} if and only if:
                        \begin{itemize}
                            \item \textbf{(Uniformity):} The subring of topologically bounded elements $R^{\circ}$ is itself bounded (in the sense that for all open neighbourhoods $U$ of $0$, there exist another open neighbourhood $V$ of $0$ such that $VR^{\circ} \subseteq U$), and 
                            \item \textbf{(Surjectivity of Frobenius):} There exists a pseudo-uniformiser $\varphi \in R^{\circ \circ}$ such that $\varphi^p \mid p$ and that the Frobenius on $R^{\circ}/\varphi$ is \textit{surjective}.
                        \end{itemize}
                \end{definition}
                \begin{example}
                    Standard examples of perfectoid fields are the topological completions of $\Q_p(p^{1/p^{\infty}}), \Q_p(\mu_{p^{\infty}}), \Q_p^{\alg}$, and $\F_p(\!(t^{1/p^{\infty}})\!)$.
                \end{example}
                
                \begin{definition}[Tilts] \label{def: tilts}
                    Let $R$ be any perfectoid ring. Then, one define its tilt - denoted by $R^{\flat}$ - as follows, wherein $R^{(n)}$ denotes the $n^{th}$ Frobenius twist of $R$:
                        $$R^{\flat} \cong \underset{n \in \N}{\lim} R^{(n)}$$
                \end{definition}
                \begin{example}
                    Different perfectoid fields can have isomorphic tilts, e.g. the tilts of both $\Q_p(p^{1/p^{\infty}})$ and $\Q_p(\mu_{p^{\infty}})$ are both isomorphic to $\F_p(\!(t^{1/p^{\infty}})\!)$. Later on, we will see that this gives rise to the moduli space of untilts (i.e. the Fargues-Fontaine Curve).
                \end{example}
                
                \begin{lemma}[Algebraic extensions of perfectoid fields]
                    Finite extensions and algebraic closures of perfectoid fields are also perfectoid.  
                \end{lemma}
                \begin{lemma}[Tilts are perfect] \label{prop: tilts_are_perfect}
                    The tilt of any perfectoid field is perfect. In fact, any perfectoid field of characteristic $p$ is perfect (in the sense that the Frobenius thereon is invertible).  
                \end{lemma}
                \begin{lemma}[Tilts are perfectoid] \label{prop: tilts_are_perfectoid}
                    A complete Tate ring of prime characteristic $p$ is perfectoid if and only if it is perfect.
                \end{lemma}
                \begin{theorem}[The Tilting Equivalence for perfectoid fields] \label{theorem: tilting_equivalence_for_perfectoid_fields}
                    For any perfectoid field $K$, there exists a canoncial adjoint-equivalence of \href{https://stacks.math.columbia.edu/tag/0BMQ}{\underline{Galois categories}}\footnote{Recall that the category of finite extensions of any field $k$ is precisely $\Sch_{/\Spec k}^{\fet}$ (which also happens to be $\Sch_{/\Spec k}^{\aff, \fet}$, since fields are of relative dimension $0$ over one another), the category of schemes finite \'etale over $\Spec k$ (see \cite[\href{https://stacks.math.columbia.edu/tag/0BL6}{Tag 0BL6}]{stacks} and \cite[\href{https://stacks.math.columbia.edu/tag/00U3}{Tag 00U3}]{stacks}).} as follows:
                        $$
                            \begin{tikzcd}
                            	{\{\text{Finite extensions of $K$}\}} & {\{\text{Finite extensions of $K^{\flat}$}\}}
                            	\arrow[""{name=0, anchor=center, inner sep=0}, "{(-)^{\flat}}"', shift right=2, from=1-1, to=1-2]
                            	\arrow[""{name=1, anchor=center, inner sep=0}, "\Witt"', shift right=2, from=1-2, to=1-1]
                            	\arrow["\dashv"{anchor=center, rotate=-90}, draw=none, from=1, to=0]
                            \end{tikzcd}
                        $$
                    wherein $\Witt$ denotes the Witt vector functor.
                \end{theorem}
                \begin{corollary}[Fontaine-Wintenberger for perfectoid fields]
                    The absolute Galois groups of any perfectoid fields is \textit{canonically} isomorphic to that of its tilt.
                \end{corollary}
                \begin{example}
                    The classical version of theorem \ref{theorem: tilting_equivalence_for_perfectoid_fields} (due to Fontaine and Wintenberger) asserts that there is a canonical isomorphism $\bfG_{\Q_p(p^{1/p^{\infty}})^{\wedge}} \cong \bfG_{\F_p(\!(t^{1/p^{\infty}})\!)^{\wedge}}$.
                \end{example}
                
            \subsubsection{Perfectoid spaces}
                \begin{definition}[Perfectoid Huber pairs] \label{def: perfectoid_huber_pairs}
                    A Huber pair $(R, R^+)$ is \textbf{perfectoid} if and only if $R$ is a perfectoid ring. 
                \end{definition}
                
                \begin{lemma}[Perfectoid Huber pairs are sheafy] \label{lemma: perfectoid_huber_pairs_are_sheafy}
                    Any perfectoid Huber pair $(R, R^+)$ is sheafy.
                \end{lemma}
                \begin{definition}[Perfectoid spaces] \label{def: perfectoid_spaces}
                    A \textbf{perfectoid space} is an adic space that is locally isomorphic to affinoid perfectoid spaces $\Spa(R, R^+)$. 
                    
                    The category of perfectoid spaces is denoted by $\Perfd$.
                \end{definition}
                \begin{proposition}[Pullbacks and products of perfectoid spaces] \label{prop: pullbacks_products_of_perfectoid_spaces}
                    Finite pullbacks and finite products exist in $\Perfd$, but there are no terminal objects (which means that products are not pullbacks). 
                \end{proposition}
                
                \begin{proposition}[Tilting glues] \label{prop: tilting_glues}
                    Let $X$ be a perfectoid space and let $U \subseteq X$ be a rational subset. Then, the Huber pair $(\calO_X(U), \calO_X^+(U))$ is perfectoid. Furthermore, one has a canonical isomorphism:
                        $$(\calO_X(U)^{\flat}, \calO_X^+(U)^{\flat}) \cong (\calO_{X^{\flat}}(U^{\flat}), \calO_{X^{\flat}}^+(U^{\flat}))$$
                    when $U$ is affinoid.
                \end{proposition}
                \begin{theorem}[The Tilting Equivalence] \label{theorem: the_tilting_equivalence}
                    \noindent
                    \begin{enumerate}
                        \item Let $S$ be an affinoid perfectoid space. Then, one has an equivalence of \'etale sites as follows, via tilting:
                        $$(\Perfd_{/X}^{\fet})_{\et} \cong (\Perfd_{/X^{\flat}}^{\fet})_{\et}$$
                        \item Let $X$ be a perfectoid space. Then, one has an equivalence of \'etale sites as follows, via tilting:
                        $$(\Perfd_{/X})_{\et} \cong (\Perfd_{/X^{\flat}})_{\et}$$
                    \end{enumerate}
                \end{theorem}